paper1_results_figs_slimmed_50_rr

### 2016-06-27 inst/documents/keep_old_insecticide.Rmd
update for new varnames

## to load previously saved runs
#   load(file=paste0(outFolder,'listOutMix_1000.rda'))
#   load(file=paste0(outFolder,'listOutI1_1000.rda'))
#   load(file=paste0(outFolder,'listOutI2_1000.rda'))

@@

load(file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
load(file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
load(file=paste0(outFolder,'listOutI2_ex2_10000.rda'))

# load(file=paste0(outFolder,'listOutMix_ex2_1000.rda'))
# load(file=paste0(outFolder,'listOutI1_ex2_1000.rda'))
# load(file=paste0(outFolder,'listOutI2_ex2_1000.rda'))

>>>>

@@

  ## to load previously saved runs  
  load(file=paste0(outFolder,'listOutMix_rr_10000.rda'))
  load(file=paste0(outFolder,'listOutI1_rr_10000.rda'))
  load(file=paste0(outFolder,'listOutI2_rr_10000.rda'))
